% LaTeX resume using res.cls
\documentclass[margin, line]{res}

\usepackage{hyperref} % URL
\usepackage{etaremune} % Backwards numbered lists 
\usepackage{marvosym} % Symbols for email, website
\usepackage{multicol} % Multiple columns for section headings
\usepackage{xcolor}	% Color
\usepackage{datetime2} % Adding the date of update at the bottom
\usepackage{indentfirst} % Paragraph indents

\definecolor{crimson}{rgb}{0.86, 0.08, 0.24}

\hypersetup{
    colorlinks=true,
    linkcolor=crimson,
    filecolor=crimson,      
    urlcolor=crimson,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
 \renewcommand{\familydefault}{\sfdefault}
\sectionskip=1.5ex plus 1ex minus -.2ex % values stolen from LaTeX
\begin{document}

\name{Jeremiah Cha}
\begin{resume}

\section{Contact}
CGIS Knafel \hfill \Letter: \href{mailto:jeremiahcha@g.harvard.edu}{jeremiahcha@g.harvard.edu}\\
1737 Cambridge St \hfill \Mundus: \href{httsp://www.jeremiahcha.com}{www.jeremiahcha.com}\\
Cambridge, MA 02138 \hfill \Mundus: \href{https://orcid.org/0000-0003-3199-3386}{orcid.org/0000-0003-3199-3386}

\section{Education}
Harvard University\\
\hspace*{5mm} Ph.D., Government \hfill Expected 2026\\
\hspace*{10mm} {\footnotesize Committee: James M. Snyder, Jr., Stephen D. Ansolabehere, Taeku Lee, Stephanie Ternullo}\\
\hspace*{5mm} A.M., Government \hfill 2022

University of California, San Diego\\
\hspace*{5mm} B.A., Political Science (High Honors), \textit{magna cum laude} \hfill 2019

\section{Peer-Reviewed Publications}
\begin{etaremune}
	\item ``Mechanisms of Checks and Balances: Appropriations, Congressional Committees, and Interbranch Conflict'' (with Jon C. Rogowski). Forthcoming. Legislative Studies Quarterly.
	\item ``Dilemmas in Representation: Immigration, Identity, and Political Parties'' (with Justin Gest and Tom K. Wong). Forthcoming. Journal of Race, Ethnicity, and Politics. 
\end{etaremune}



\section{Working Papers}
\begin{etaremune}
	\item ``Who Governs Now? Racial Representation and the Politics of Urban Space''
	\item ``Measuring Issue Racialization''
	\item ``What School Boards Talk About When They Talk about Race (with Hunter Rendleman and Tyler Simko)'' 
\end{etaremune}

\section{Selected Works \\in Progress}
\begin{etaremune}
	\item ``Revisiting Committee Politics (with Sooahn Shin)''
	\item ``Drawing Blanks: Redistricting and Turnout Effects'' (with Angelo Dagonel and Kiara Hernandez)
	\item ``The Direct Primary Election'' (with James M. Snyder, Jr.)
\end{etaremune}

\section{Data}
\begin{etaremune}
	\item Cha, Jeremiah, Shiro Kuriwaki, and James M. Snyder, Jr. (2024). ``Candidates in American General Elections.'' Harvard Dataverse. \textsc{doi}: \href{https://doi.org/10.7910/DVN/DGDRDT}{\texttt{10.7910/DVN/DGDRDT}}.
\end{etaremune}

\section{Non-refereed Publications}
\begin{etaremune}
	\item Devlin, Kat, Regina Widjaya and Jeremiah Cha. 2020. ``For Global Legislators on Twitter, an Engaged Minority Creates Outsize Share of Content.'' Pew Research Center.
	\item Cha, Jeremiah. 2020. ``Fast facts about South Koreans’ views of democracy as legislative election nears.'' Pew Research Center.
	\item Cha, Jeremiah. 2020. ``People in Asia-Pacific regard the U.S. more favorably than China, but Trump gets negative marks.'' Pew Research Center.
	\item Huang, Christine and Jeremiah Cha. 2020. ``Russia and Putin receive low ratings globally.'' Pew Research Center.
	\item Fetterolf, Janell and Jeremiah Cha. 2020. ``Few in other countries approve of Trump’s major foreign policies, but Israelis are an exception.'' Pew Research Center.
	\item Wong, Tom K., Jeremiah Cha and Erika Villareal-Garcia. 2019. ``The Impact of Changes to the Public Charge Rule on Undocumented Immigrants Living in the United States.'' U.S. Immigration Policy Center (USIPC) at UC San Diego.
	\item Silver, Laura, Emily A. Vogels, Mara Mordecai, Jeremiah Cha, Raea Rasmussen and Lee Rainie. 2019. ``Mobile Divides in Emerging Economies.'' Pew Research Center.
	\item Cha, Jeremiah. 2017. ``Dreaming of DACA.'' Claremont Journal of Law and Public Policy.
\end{etaremune}


\section{Fellowships, Grants and \\Awards}


Honorable Mention, Bryan Jackson Dissertation Award \hfill 2025\\
\hspace*{5mm} \textit{APSA Urban and Local Politics Section} \\
Pre-Doctoral Fellow, Election Law Clinic \hfill 2025\\
\hspace*{5mm} \textit{Harvard Law School}\\
Teaching Recognition \hfill 2023, 2024\\
\hspace*{5mm} \textit{Harvard Undergraduate Association}\\
CAPS Seed Grant (with Angelo Dagonel and Kiara Hernandez)\hfill 2022\\
\hspace*{5mm} \textit{Harvard University Center for American Political Studies}\\
Harvard GSC Conference Grant \hfill 2022\\
\hspace*{5mm} \textit{Harvard University GSAS}\\
V.O. Key Fellowship \hfill 2020 - 2024\\
\hspace*{5mm} \textit{Harvard University GSAS}\\
Phi Beta Kappa \hfill 2019\\
Pi Sigma Alpha \hfill 2017

\section{Selected \\Presentations}
APSA \hfill 2023, 2024, 2025\\
MPSA \hfill 2023, 2024, 2025\\
Tufts University \hfill Apr 2023\\
Pew Research Center  \hfill June 2020

\section{Teaching \\and Advising}
Harvard College, Department of Government\\
\hspace*{5mm} GOV 30, American Government: A New Perspective (Head TF) \hfill Fall 2023, 2024\\
\hspace*{5mm} GOV 51, Data Analysis and Politics, (TF) \hfill Spring 2023, 2024\\
\hspace*{5mm} GOV 30, American Government: A New Perspective,  (TF) \hfill Fall 2022

\hspace*{2.5mm} Thesis Advising \\
\hspace*{5mm} Jack Holland \hfill Harvard '26\\
\hspace*{5mm} Aaron Shuchman (Government) \hfill Harvard '25\\
\hspace*{5mm} Ava Pallotta (Government) \hfill Harvard '25\\
\hspace*{5mm} Oliver Adler (Government) \hfill Harvard '24

\section{Service}
Harvard University\\
\hspace*{5mm} American Politics Speaker Series Coordinator \hfill 2022-2023, 2024-2025\\
\hspace*{5mm} Diversity Committee, Harvard University \hfill 2020 - 2024\\
\hspace*{5mm} American Politics Research Workshop Coordinator \hfill 2022 - 2023\\
\hspace*{5mm} Communications Officer, Harvard Government GSA \hfill 2022 - 2023\\
\hspace*{5mm} Rules and Election Officer, Harvard Government GSA \hfill 2021 - 2023\\

\section{Non-Academic Experience}
Brookings Institution, Governance Studies \hfill 2018
House of Representatives, Intern \hfill 2017\\
House of Representatives, Intern \hfill 2016\\
Chaminade College Prep High School, Debate Coach \hfill 2015 - 2018

\section{Skills}
Technical: \texttt{R}, Python, Stata, SPSS, \LaTeX, HTML\\
Language: English (Native), Korean (Limited Working)

\vspace*{\fill}

\hfill \small{\textit{Updated \today}}

\end{resume}
\end{document}
